---
title: "Biology-4315: Lab2 Git Practice"
author: "Gavin Ieong"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Section One:More Packages (ggplot2 and vegan)

Start by loading the vegan and ggplot2 packages
```{r libs,warning=FALSE, message=FALSE}

library('vegan')
library('ggplot2')
```

Next, we will put the dune dataet into a variable called dune2 and log1p transform it
```{r dataset1}
data(dune)
dune2 <- dune
log1p(dune2)
```

Now, we will perform nmds on dune2 using the function metaMDS
and assign it to a new variable. 
We will then access the points and assign it to dpoints
```{r dataset2}
new_dune2 <- metaMDS(dune2)
dpoints <- as.data.frame(new_dune2$points)
dpoints
```

Finally, we will plot a ggplot using mds1 as my x, and mds2 as my y
We will set the theme to black and white, and give it a title as well
Then we will save the plot as a pdf

```{r plot}
pdf("myplot.pdf")
ggplot(dpoints, aes(x=MDS1, y =MDS2), )+geom_point()+theme_bw() + ggtitle("Plot of MDS1 and MDS2 From dpoints")
dev.off()
```

